---
title: "Plotly Package Review"
author: "Lindsey Norberg"
date: "10/4/2020"
output:
  html_document:
    toc: TRUE
    theme: cosmo
    toc_float: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
```

# Plotly Package Overview

## What is Plotly? 

Plotly is a data visualization package that is used to create advanced and publication-quality interactive graphics.   

## Why use Plotly? 

Data visualization acts as an accentuating yet critical component of data science. Although quantitative analysis and technical knowledge drive the extraction of insight from data, perhaps what acts as a just as equal, if not more, counterpart is the presentation of findings. Data visualization perfectly accenuates data analytics, as it allows for data scientists to visually present and communicate important findings within the data in a digestible manner to key stakeholders. Traditional data visualization packages, such as ggplot2 or plotting functions within native R, provide means and methods of accomplishing this. However, plotly's value proposition is the ability to expound upon tradition two dimensional plotting techniques by offering interactivity and dimensionality that allows both data scientists and key stakeholders alike to extract more complex and meaningful insights, beyond what is capable in 2d graphics. 

## History of Plotly

Plotly 

### Some Important Info About Plotly {.tabset}

For an in-depth overview of the plotly package, click [here](https://cran.r-project.org/web/packages/plotly/index.html).

#### Version History

```{r, echo = FALSE}
table <- data.frame('Current Version' = '4.9.2.1')
kable(table)
```


#### Usage

#### Dependencies 
- R (≥ 3.2.0) - R version 3.2.0 or later
- ggplot2 (≥ 3.0.0) - ggplot2 version 3.0.0 or later

#### Imports (Exogenous Package Use)
- tools
- scales 
- httr 
- jsonlite (≥ 1.6)
- magrittr 
- digest 
- viridisLite 
- base64enc 
- htmltools (≥ 0.3.6) 
- htmlwidgets (≥ 1.3) 
- tidyr, hexbin 
- RColorBrewer 
- dplyr 
- tibble 
- lazyeval (≥ 0.2.0) 
- rlang 
- crosstalk 
- purrr 
- data.table 
- promises



